Artin Group Presentations Arising from Cluster Algebras

### 2014-08-03 Paper.tex
Small Changes to Section 5

\begin{proof}
It suffices to prove that the relation t(0, 1) implies the relation t(d-1, 0), as the other relations will follow by induction. So suppose $A_{\Gamma}$ satisfies the relation t(0, 1). Then we have
\begin{align*}
s_{d-1}p_{d-1, 0} & = s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} &\text{by (T2)} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by t(0, 1)}\\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} = p_{d-1, 0}s_{d-1}
\end{align*}
as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
\end{proof}
Furthermore, we obtain similar results for cycles containing edges of weight 2.
\begin{lem} \label{2tri}
Let $\Gamma$ be a diagram of finite type containing the following 3-cycle:

@@

\begin{proof}
The lemma follows from the fact that
\begin{align*}
& s_{k}^{-1}s_{j}(s_{i}p_{i, j}s_{i}^{-1}p_{i, j}^{-1})s_{j}^{-1}s_{k} \\
& s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
&= s_{k}^{-1}s_{j}s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1} \\
&= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i} \\
&= s_{k}^{-1}p_{k, i}s_{k}p_{k, i}^{-1}
\end{align*}
\end{proof}

@@

\begin{lem}\label{lem:extra_square_relation}
Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that
$$s_{j}p_{j, k}s_{j}p_{j, k}^{-1}s_{j}^{-1}p_{j, k}^{-1} := s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
\end{lem}

@@

\begin{proof}
We have that
\begin{align*}
& s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}p_{i, j}s_{i}^{-1}p_{i, j}^{-1})s_{j}^{-1}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{l}^{-1}s_{k}s_{j})s_{j}^{-1}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}(s_{j}s_{i}s_{j}^{-1})(s_{k}^{-1}s_{l}s_{k})(s_{j}s_{i}^{-1}s_{j}^{-1})s_{k}^{-1}s_{l}^{-1}s_{k}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{k}^{-1}(s_{l}^{-1}s_{k}s_{l})s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{l} \\
&= s_{k}^{-1}p_{k, l}s_{k}p_{k, l}^{-1}
\end{align*}
\end{proof}

>>>>

\begin{proof}
It suffices to prove that the relation t(0, 1) implies the relation t(d-1, 0), as the other relations will follow by induction. So suppose $A_{\Gamma}$ satisfies the relation t(0, 1). Then we have
\begin{align*}
s_{d-1}p(d-1, 0) & = s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} &\text{by (T2)} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by t(0, 1)}\\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} &\text{by (T2)}\\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} = p(d-1, 0)s_{d-1}
\end{align*}
as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
\end{proof}
Furthermore, we obtain similar results for cycles containing edges of weight 2.
\begin{lem} \label{2tri}
Let $\Gamma$ be a diagram of finite type containing the following 3-cycle:

@@

\begin{proof}
The lemma follows from the fact that
\begin{align*}
& s_{k}^{-1}s_{j}(s_{i}p(i, j)s_{i}^{-1}p(i, j)^{-1})s_{j}^{-1}s_{k} \\
& s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
&= s_{k}^{-1}s_{j}s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1} \\
&= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i} \\
&= s_{k}^{-1}p(k, i)s_{k}p(k, i)^{-1}
\end{align*}
\end{proof}

@@

\begin{lem}\label{lem:extra_square_relation}
Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that
$$s_{j}p(j, k)s_{j}p(j, k)^{-1}s_{j}^{-1}p(j, k)^{-1} := s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
\end{lem}

@@

\begin{proof}
We have that
\begin{align*}
& s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}p(i, j)s_{i}^{-1}p(i, j)^{-1})s_{j}^{-1}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{l}^{-1}s_{k}s_{j})s_{j}^{-1}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}(s_{j}s_{i}s_{j}^{-1})(s_{k}^{-1}s_{l}s_{k})(s_{j}s_{i}^{-1}s_{j}^{-1})s_{k}^{-1}s_{l}^{-1}s_{k}s_{l}s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{k}^{-1}(s_{l}^{-1}s_{k}s_{l})s_{k} \\
&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{l} \\
&= s_{k}^{-1}p(k, l)s_{k}p(k, l)^{-1}
\end{align*}
\end{proof}
